### 2017-02-08 manuscript.rmd
reformatted with new bib, cherry picked bm model parameters to reduce memory footprint

	#' Estimate Tau evolution parameters from a tree::treedata tree
	#' and add them back into the tree object.
	#' 
	#' @param nhx A phylogenetic tree and associated Tau values 
	#' as a treeio::treedata object
	#' @param ... Additional arguments to pass to geiger::fitContinuous()
	#' @return A phylogenetic trees as a treeio::treedata object, 
	#' with estimated brownian motion model parameters stored 
	#' in @phylo$model
	#' @export
	add_model_parameters = function( nhx, ... ) {
		phy = nhx@phylo
		tau_original = nhx@data$Tau [ 1:length( phy$tip.label ) ]
		names( tau_original ) = phy$tip.label
		nhx@phylo$model = fitContinuous( phy, tau_original, ... )

>>>>

	#' Estimate Tau evolution parameters from a tree::treedata tree
	#' and add them back into the tree object.
	#' 
	#' @param nhx A phylogenetic tree and associated Tau values 
	#' as a treeio::treedata object
	#' @param ... Additional arguments to pass to geiger::fitContinuous()
	#' @return A phylogenetic trees as a treeio::treedata object, 
	#' with estimated brownian motion model parameters stored 
	#' in @phylo$model
	#' @export
	add_model_parameters = function( nhx, ... ) {
		phy = nhx@phylo
		tau_original = nhx@data$Tau [ 1:length( phy$tip.label ) ]
		names( tau_original ) = phy$tip.label
		brownian_model = fitContinuous( phy, tau_original, ... )

		nhx@phylo$model$opt$z0 = brownian_model$opt$z0
		nhx@phylo$model$opt$sigsq = brownian_model$opt$sigsq
